### 2025-01-28 paper/sections/appendix.qmd
the joys of quarto and julia and latex and shootme

---
engine: julia
julia: 
  exeflags: ["--project=experiments/"]
---

```{julia}
cd("../")

using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.StatsBase
using DotEnv

>>>>

```{julia}
using CTExperiments
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.StatsBase
using DotEnv
